Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-25 paper/ICPC19/icpc19.tex
another commit 2
small fix

@@

@@

In this section, the methodology used to measure the impact of security refactorings on the maintainability of open-source software is presented in depth in the following sections and illustrated in Figure \ref{fig:met}. Aiming to answer the research questions presented in this paper, we use a dataset containing $716$ security refactorings collected from open-source software available on GitHub. $648$ of those refactorings were reported in a previous study conducted in 2017 \cite{Reis:2017:IJSSE}. In parallel, a baseline of regular commits was randomly collected from the list of projects of the main dataset to evaluate what is the impact of regular commits on the maintainability of open-source software. The Software Improvement Group's\footnote{SIG's website is available at https://www.softwareimprovementgroup.com/ (Accessed on January 23, 2019)} web-based source code analysis service Better Code Hub (BCH) \footnote{BCH's website is available at https://bettercodehub.com/ (Accessed on January 23, 2019)} was used to collect the maintainability reports for both security and regular commits.

@@

Table \ref{tab:dataset} presents the final dataset projects statistics. Refactorings from 94 projects were evaluated by BCH. According to the statistics, the projects of this dataset are popular and the developers are active.

>>>>

\usepackage{listings}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{lightgreen}{rgb}{0.6,0.9,0.6}
\definecolor{lightyellow}{rgb}{0.9,0.9,0.6}
\definecolor{lightorange}{rgb}{0.9,0.8,0.6}
\definecolor{lightred}{rgb}{0.9,0.7,0.7}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{lightgray}{rgb}{0.8,0.8,0.8}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\usepackage{pifont}
\newcommand{\lstbg}[3][0pt]{{\fboxsep#1\colorbox{#2}{\strut #3}}}
\lstset{ %
  language=Java,
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
  breaklines=false,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray}\bfseries,    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
  frame=single,
  escapeinside={/*!}{!*/},
  morekeywords={@Override,@TargetApi},
  moredelim=**[l][\color{mygreen}]{+},
  moredelim=*[l][\color{red}]{-}
}

@@

%\lstinputlisting[language=Python]{source_filename.py}

@@

In this section, the methodology used to measure the impact of security refactorings on the maintainability of open-source software is presented in depth in the following sections and illustrated in Figure \ref{fig:met}. Aiming to answer the research questions presented in this paper, we use a dataset containing $716$ security refactorings collected from open-source software available on GitHub. $648$ of those refactorings were reported in a previous study conducted in 2017 \cite{Reis:2017:IJSSE}. In parallel, a baseline of regular commits was randomly collected from the list of projects of the main dataset to evaluate what is the impact of regular commits on the maintainability of open-source software. The Software Improvement Group's\footnote{SIG's website is available at https://www.sig.eu/ (Accessed on January 23, 2019)} web-based source code analysis service Better Code Hub (BCH) \footnote{BCH's website is available at https://bettercodehub.com/ (Accessed on January 23, 2019)} was used to collect the maintainability reports for both security and regular commits.

@@

Table \ref{tab:dataset} presents the final dataset projects statistics. Refactorings from 94 projects were evaluated by BCH. According to the statistics, the projects of this dataset are \textcolor{mypink3}{popular and the developers are active}.
